Improving Haskell Types with SMT

### 2015-07-18 docs/paper.tex
Fix typos

The approach presented in this paper uses similar tools---namely
SMT solvers---to Liquid Haskell \cite{liquid-haskell}. However,
the design and overall goals of the two techniques are somewhat
different and, indeed, it makes perfect sense to use both systems
in a single project.  Liquid Haskell enables Haskell programmers
to augment Haskell definitions with refinements of the types,
which may be used to verify various properties of the program.
The refinment language is separate from the language of Haskell
types---it is quite expressive, and is really aimed at formal
verification.  As such, a function will have its ordinary
type and, in addition, a refinment type, which serves to specify
some aspect of the behavior of the function.  The checks performed
by Liquid Haskell are entirely separate from the ones performed
by GHC's type checker.  This is quite different from the
technuqe described in this paper, which shows how to integrate
an SMT solver directly into GHC's type chcker.  The benefit of
of extending GHC's type chcker is that we don't need to
introduce a separate language for specifications, instead
we may reuse types directly.  Ultimately, however, the two
approaches are not at all mutually exclusive.  The next
section gives a brief flavor of what can be achieved using
the technieques from this paper.

@@

For example, the constraint \Verb"(F 3 + 4) ~ 7" will be imported as
\Verb"(x + 4) ~ 7", and we will remember that \Verb"x" stands for \Verb"F 3".
Later on, if we need to return results to the core GHC solver that mention
\Verb"x", we replace it by the orignal expression, \Verb"F 3".

>>>>

The approach presented in this paper uses similar tools---namely
SMT solvers---to Liquid Haskell \cite{liquid-haskell}. However,
the design and overall goals of the two techniques are somewhat
different and, indeed, it makes perfect sense to use both systems
in a single project.  Liquid Haskell enables Haskell programmers
to augment Haskell definitions with refinements of the types,
which may be used to verify various properties of the program.
The refinement language is separate from the language of Haskell
types---it is quite expressive, and is really aimed at formal
verification.  As such, a function will have its ordinary
type and, in addition, a refinement type, which serves to specify
some aspect of the behavior of the function.  The checks performed
by Liquid Haskell are entirely separate from the ones performed
by GHC's type checker.  This is quite different from the
technique described in this paper, which shows how to integrate
an SMT solver directly into GHC's type checker.  The benefit of
of extending GHC's type checker is that we don't need to
introduce a separate language for specifications, instead
we may reuse types directly.  Ultimately, however, the two
approaches are not at all mutually exclusive.  The next
section gives a brief flavor of what can be achieved using
the techniques from this paper.

@@

For example, the constraint \Verb"(F 3 + 4) ~ 7" will be imported as
\Verb"(x + 4) ~ 7", and we will remember that \Verb"x" stands for \Verb"F 3".
Later on, if we need to return results to the core GHC solver that mention
\Verb"x", we replace it by the original expression, \Verb"F 3".
